---
title: "Data "
output: html_document
---

#0-Configuración

##0.1-Configuration BigQuery
```{r preprocessing, warning=F, message=F, echo=F}
## Preprocessing
library(bigrquery)
library(dplyr)
library(ggplot2)
con <- dbConnect(
#  bigrquery::bigquery(),
#  project = <project_id>,
#  dataset = <dataset_id>,
#  billing = <billing_id>
)
""
# Store the project id
#projectid = <project_id>
```

#1-Load and Tidy Datasets
##1.1-Load all data relevant to session, user and country that I will use as a base
```{r preprocessing, warning=F, message=F, echo=F}
## Preprocessing
# Set your query
sql <- " 
    SELECT
        param.value.int_value AS ga_session_id,
        user_pseudo_id,
        user_id,
        event_date,
        geo.country
    FROM 
        `<project_id>.<dataset_id>.events_*`,
        UNNEST(event_params) AS param
    WHERE 
        param.key = 'ga_session_id'
    AND
        param.value.int_value IS NOT NULL
"

# Run the query and store the data in a tibble
sessions <- bq_project_query(projectid, sql)

# Download the data into a tibble
sessions_data <- bq_table_download(sessions)

sessions_data
```
##1.2-Load all experiment case data per session
###1.2.1-Retrieve experiment data from BigQuery
```{r preprocessing, warning=F, message=F, echo=F}
## Preprocessing
# Set your query
sql <- "
    SELECT
        param1.value.int_value AS ga_session_id,
        param2.value.int_value AS experiment_case
    FROM 
        `<project_id>.<dataset_id>.events_*`,
        UNNEST(event_params) AS param1,
        UNNEST(user_properties) AS param2
    WHERE 
        param1.key = 'ga_session_id' AND
        param2.key= 'experiment_case'
"

# Run the query and store the data in a tibble
experiments <- bq_project_query(projectid, sql)

# Download the data into a tibble
experiments_data <- bq_table_download(experiments)

experiments_data
```

###1.2.2-Wrangle data to get only the sessions with its associated experiment_case, then I made sure that sessions with more than 1 experiment case would be filter
```{r preprocessing, warning=F, message=F, echo=F}
## Here I am checking that I am only counting the sessions that contain only 1 experiment case
experiment_data_tidy <- experiments_data %>% 
  group_by(ga_session_id) %>% 
  summarise(experiment_case =unique(experiment_case)) %>% 
  group_by(ga_session_id) %>% 
  summarise(instances_of_unique_experiment_case = n()) %>% 
  #Here I am filtering out all sessions with more than one type of experiment case
  filter(instances_of_unique_experiment_case == 1)

## Here I am joining the experiment case number knowing that all sessions were expose to a single case
experiment_data_tidy <-experiment_data_tidy %>% 
  left_join(experiments_data, by = 'ga_session_id') %>% 
  group_by(ga_session_id) %>% 
  summarise(experiment_case = unique(experiment_case))

experiment_data_tidy
```











##1.3-Load all time expend in producer and engagement time case data per session
###1.3.1-Retrieve data from BigQuery
```{r preprocessing, warning=F, message=F, echo=F}
## Preprocessing
# Set your query
sql <- "
SELECT 
  param1.value.int_value AS ga_session_id,
  param2.value.double_value AS time_spent_in_producer,
  param3.value.int_value AS engagement_time_msec
FROM `<project_id>.<dataset_id>.events_*`,
  UNNEST(event_params) AS param1,
  UNNEST(event_params) AS param2,
  UNNEST (event_params) AS param3
WHERE event_name = 'page_unload'
    AND param1.key = 'ga_session_id'
    AND param2.key = 'timeSpentInProducer'
    AND param3.key = 'engagement_time_msec'
"

# Run the query and store the data in a tibble
time_producer_and_engagement <- bq_project_query(projectid, sql)

# Download the data into a tibble
time_producer_and_engagement_data <- bq_table_download(time_producer_and_engagement)

time_producer_and_engagement_data
```

###1.3.2-Wrangle data to sum times
```{r preprocessing, warning=F, message=F, echo=F}
time_producer_and_engagement_data_tidy <-time_producer_and_engagement_data %>% 
  mutate(time_spent_in_producer = if_else(is.na(time_spent_in_producer),0,time_spent_in_producer)) %>% 
  group_by(ga_session_id) %>% 
  summarise(sum_in_producer = sum(time_spent_in_producer),
            sum_engagement =sum(engagement_time_msec)/1000) 

time_producer_and_engagement_data_tidy
```

##1.4-Load all time expend in experiment modal and other click events
###1.4.1-Retrieve data from time in moddal from BigQuery
```{r preprocessing, warning=F, message=F, echo=F}
## Preprocessing
# Set your query
sql <- "
SELECT 
  param1.value.int_value AS ga_session_id,
  param2.value.string_value AS button_ID,
  param3.value.double_value AS timeSpentInExperimentModal
FROM `<project_id>.<dataset_id>.events_*`,
  UNNEST(event_params) AS param1,
  UNNEST(event_params) AS param2,
  UNNEST (event_params) AS param3
WHERE event_name = 'button_clicked'
    AND param1.key = 'ga_session_id'
    AND param2.key = 'button_ID'
    AND param3.key = 'timeSpentInExperimentModal'
"

# Run the query and store the data in a tibble
time_in_modal <- bq_project_query(projectid, sql)

# Download the data into a tibble
time_in_modal_data <- bq_table_download(time_in_modal)

time_in_modal_data
```
###1.4.2-Wrangle data to sum time in modal
```{r preprocessing, warning=F, message=F, echo=F}

time_in_modal_data_tidy <- time_in_modal_data %>% 
  group_by(ga_session_id) %>% 
  summarise(time_in_modal = sum(timeSpentInExperimentModal)) %>% 
  mutate(time_in_modal = if_else(is.na(time_in_modal),0,time_in_modal))


```
##1.5-Load all add to cart data
```{r preprocessing, warning=F, message=F, echo=F}
## Preprocessing
# Set your query
sql <- "
SELECT 
  param1.value.int_value AS ga_session_id,
  param2.item_id,
  param3.item_name,
  param4.item_brand,
  param5.price
FROM `<project_id>.<dataset_id>.events_*`,
  UNNEST(event_params) AS param1,
  UNNEST(items) AS param2,
  UNNEST(items) AS param3,
  UNNEST(items) AS param4,
  UNNEST(items) AS param5
WHERE event_name = 'add_to_cart'
    AND param1.key = 'ga_session_id'
"

# Run the query and store the data in a tibble
add_to_cart <- bq_project_query(projectid, sql)

# Download the data into a tibble
add_to_cart_data <- bq_table_download(add_to_cart)

add_to_cart_data
```
###1.4.2-Wrangle add to cart data
```{r preprocessing, warning=F, message=F, echo=F}

add_to_cart_data_tidy <- add_to_cart_data %>% 
  mutate(price = if_else(is.na(price),0,price)) %>% 
  group_by(ga_session_id) %>% 
  summarise(amount_of_add_to_cart = n_distinct(item_id),
            amount_of_unique_producers = n_distinct(item_brand),
            value_of_all_products_added = sum(price))

add_to_cart_data_tidy

```

##1.6-Load all begin checkout data
```{r preprocessing, warning=F, message=F, echo=F}
## Preprocessing
# Set your query
sql <- "
SELECT 
  param1.value.int_value AS ga_session_id,
  param2.value.int_value AS value,
  ecommerce.total_item_quantity AS unique_items
FROM `<project_id>.<dataset_id>.events_*`,
  UNNEST(event_params) AS param1,
  UNNEST(event_params) AS param2
WHERE event_name = 'begin_checkout'
    AND param1.key = 'ga_session_id'
    AND param2.key = 'value'
"

# Run the query and store the data in a tibble
begin_checkout <- bq_project_query(projectid, sql)

# Download the data into a tibble
begin_checkout_data <- bq_table_download(begin_checkout)

begin_checkout_data
```
###1.6.2-Wrangle begin checkout data
```{r preprocessing, warning=F, message=F, echo=F}

begin_checkout_data_tidy <- begin_checkout_data %>% 
  group_by(ga_session_id) %>% 
  summarise(value_begin_checkout = max(value),
            unique_items_begin_checkout = max(unique_items),
            check_out_boolean = as.integer(1))

begin_checkout_data_tidy

```



##1.7-Load all begin purchase
```{r preprocessing, warning=F, message=F, echo=F}
## Preprocessing
# Set your query
sql <- "
SELECT 
  param1.value.int_value AS ga_session_id,
  event_date AS event_date,
  param3.value.string_value AS transaction_id,
  param2.value.int_value AS value,
  ecommerce.total_item_quantity AS unique_items
FROM `<project_id>.<dataset_id>.events_*`,
  UNNEST(event_params) AS param1,
  UNNEST(event_params) AS param2,
  UNNEST(event_params) AS param3
WHERE event_name = 'purchase'
    AND param1.key = 'ga_session_id'
    AND param2.key = 'value'
    AND param3.key = 'transaction_id'
"

# Run the query and store the data in a tibble
purchase <- bq_project_query(projectid, sql)

# Download the data into a tibble
purchase_data <- bq_table_download(purchase)

purchase_data
```
###1.7.2-Wrangle purchase checkout data
```{r preprocessing, warning=F, message=F, echo=F}

purchase_data_tidy <- purchase_data %>% 
  mutate(event_date = as.Date(event_date, format = "%Y%m%d")) %>% 
  group_by(ga_session_id) %>% 
  summarise(purchase_date = max(event_date),
            value_purchase = max(value),
            unique_items_purchase = max(unique_items),
            purchase_boolean = as.integer(1))

purchase_data_tidy
```



#2-Join and tidy all datasets into a single dataframe
```{r preprocessing, warning=F, message=F, echo=F}

# Here I am joining the experiment case and time in producer to the sessions dataframe
sessions_data_tidy <- sessions_data %>% 
  left_join(experiment_data_tidy,by='ga_session_id',) %>% 
  left_join(time_producer_and_engagement_data_tidy,by='ga_session_id') %>% 
  left_join(time_in_modal_data_tidy, by='ga_session_id') %>% 
  left_join(add_to_cart_data_tidy, by='ga_session_id') %>%
  left_join(begin_checkout_data_tidy, by='ga_session_id' ) %>% 
  left_join(purchase_data_tidy, by='ga_session_id' ) %>% 
  # Tidy data 
  mutate(experiment_case = as.character(if_else(is.na(experiment_case),-1,experiment_case)),
         sum_in_producer = if_else(is.na(sum_in_producer),0,sum_in_producer),
         sum_engagement = if_else(is.na(sum_engagement),0,sum_engagement),
         user_id = if_else(is.na(user_id),'-1',user_id),
         time_in_modal = if_else(is.na(time_in_modal),0,time_in_modal),
         event_date = as.Date(event_date, format = "%Y%m%d"),
         amount_of_add_to_cart = if_else(is.na(amount_of_add_to_cart),0,amount_of_add_to_cart),
         amount_of_unique_producers = if_else(is.na(amount_of_unique_producers),0,amount_of_unique_producers),
         value_of_all_products_added = if_else(is.na(value_of_all_products_added),0,value_of_all_products_added)
         ) %>% 
  # Then aggregate the data per session
  group_by(ga_session_id) %>% 
  summarise(user_pseudo_id = unique(user_pseudo_id),
            user_id = unique(user_id),
            event_date = unique(event_date),
            country = unique(country),
            experiment_case = unique(experiment_case),
            sum_in_producer = sum(sum_in_producer),
            sum_engagement = sum(sum_engagement),
            time_in_modal = max(time_in_modal),
            amount_of_add_to_cart = max(amount_of_add_to_cart),
            amount_of_unique_producers = max(amount_of_unique_producers),
            value_of_all_products_added = max(value_of_all_products_added),
            begin_checkout_boolean = max(check_out_boolean),
            begin_checkout_value = max(value_begin_checkout),
            begin_checkout_amount_items = max(unique_items_begin_checkout),
            purchase_boolean = max(purchase_boolean),
            purchase_value = max(value_purchase),
            purchase_amount_items = max(unique_items_purchase),
            min_purchase_date = min(purchase_date)
            ) %>% 
  mutate(begin_checkout_boolean = if_else(is.na(begin_checkout_boolean),0,begin_checkout_boolean),
         begin_checkout_value = if_else(is.na(begin_checkout_value),0,begin_checkout_value),
         begin_checkout_amount_items = if_else(is.na(begin_checkout_amount_items),0,begin_checkout_amount_items),
         purchase_boolean = if_else(is.na(purchase_boolean),0,purchase_boolean),
         purchase_value = if_else(is.na(purchase_value),0,purchase_value),
         purchase_amount_items = if_else(is.na(purchase_amount_items),0,purchase_amount_items),
         min_purchase_date = if_else(is.na(min_purchase_date),coalesce(min_purchase_date, Sys.Date()),min_purchase_date)) %>% 
  filter(!is.na(as.integer(user_id)))#I get rid of the one instance where there non integer values

sd = 3*sd(sessions_data_tidy$sum_in_producer)


#I add all the known users from different devices
users_id_data_tidy <- sessions_data_tidy %>% 
  group_by(user_id) %>% 
  summarise(user_pseudo_id =max(user_pseudo_id),
            max_event_date = max(event_date),
            min_event_date = min(event_date),
            experiment_case = max(experiment_case),
            country = max(country),
            amount_of_session = n(),
            sum_in_producer=sum(sum_in_producer),
            sum_engagement=sum(sum_engagement),
            time_in_modal = sum(time_in_modal),
            amount_of_add_to_cart = sum(amount_of_add_to_cart),
            amount_of_unique_producers = sum(amount_of_unique_producers),
            value_of_all_products_added = sum(value_of_all_products_added),
            amount_of_checkouts = sum(begin_checkout_boolean),
            value_of_checkouts = sum(begin_checkout_value),
            items_in_checkouts = sum(begin_checkout_amount_items),
            amount_of_purchases = sum(purchase_boolean),
            value_of_purchases = sum(purchase_value),
            items_in_purchases = sum(purchase_amount_items),
            min_purchase_date = min(min_purchase_date)) %>% 
  filter(as.integer(user_id)>=1)

# Here I create the df that summarises the information per user
users_data_tidy <- sessions_data_tidy %>%  
  group_by(user_pseudo_id) %>% 
  summarise(user_id =max(user_id),
            max_event_date = max(event_date),
            min_event_date = min(event_date),
            experiment_case = max(experiment_case),
            country = max(country),
            amount_of_session = n(),
            sum_in_producer=sum(sum_in_producer),
            sum_engagement=sum(sum_engagement),
            time_in_modal = sum(time_in_modal),
            amount_of_add_to_cart = sum(amount_of_add_to_cart),
            amount_of_unique_producers = sum(amount_of_unique_producers),
            value_of_all_products_added = sum(value_of_all_products_added),
            amount_of_checkouts = sum(begin_checkout_boolean),
            value_of_checkouts = sum(begin_checkout_value),
            items_in_checkouts = sum(begin_checkout_amount_items),
            amount_of_purchases = sum(purchase_boolean),
            value_of_purchases = sum(purchase_value),
            items_in_purchases = sum(purchase_amount_items),
            min_purchase_date = min(min_purchase_date)) %>% 
  filter(!as.integer(user_id)>=1) %>% 
  bind_rows(users_id_data_tidy) #apend the users with id


#experiment_data_tidy
#time_producer_and_engagement_data_tidy
```

#3 Define Data for Data Analysis HERE!!!
#3.1. Filter the data and define variables in a single place here
```{r preprocessing, warning=F, message=F, echo=F}
#Filter all users that had purchases before this date
variable_min_event_date =  as.Date('2023-09-01')

#Filter all users that had events before this date
variable_max_event_date = as.Date('2024-01-01')

#Filter all users that stay extremly long time in producers
#In case I need to filter after certaing amount of time in producer (I should change this to get rid of outliers in time_in_producer)
variable_outlier_sum_in_producer = 3*sd(users_data_tidy_filtered$sum_in_producer)
variable_outlier_sessions = 3*sd(users_data_tidy_filtered$amount_of_session)
variable_outlier_purchase = 3*sd(users_data_tidy_filtered$value_of_purchases)


users_data_tidy_filtered <- users_data_tidy %>% 
  filter(country == 'Costa Rica',
         experiment_case != -1,
         min_event_date >= variable_min_event_date,
         min_event_date < variable_max_event_date,) %>%
  arrange(min_event_date)


users_data_tidy_filtered
```
#3.2 - Look at the filtered data
```{r preprocessing, warning=F, message=F, echo=F}
# Here I am just exploring the data
users_data_tidy_filtered %>%
  group_by(experiment_case) %>% 
  summarise(amount_of_users = n(),
            total_amount_session = sum(amount_of_session),
            total_time_producer = sum(sum_in_producer),
            total_engagement = sum(sum_engagement),
            sum_time_in_modal = sum(time_in_modal),
            sum_amount_of_add_to_cart = sum(amount_of_add_to_cart),
            sum_amount_of_unique_producers = sum(amount_of_unique_producers),
            sum_value_of_all_products_added = sum(value_of_all_products_added),
            sum_amount_of_checkouts = sum(amount_of_checkouts),
            sum_value_of_checkouts = sum(value_of_checkouts),
            sum_items_in_checkots = sum(items_in_checkouts),
            sum_amount_of_purchases = sum(amount_of_purchases),
            sum_value_of_purchases = sum(value_of_purchases),
            sum_items_in_purchases = sum(items_in_purchases))

users_data_tidy_filtered %>% 
  group_by(experiment_case) %>% 
  summarise(amount_of_users = n(),
            amount_of_logged_in_users = n_distinct(user_id),
            mean_amount_session = mean(amount_of_session),
            mean_time_producer = mean(sum_in_producer),
            mean_engagement = mean(sum_engagement),
            mean_time_in_modal = mean(time_in_modal),
            mean_amount_of_add_to_cart = mean(amount_of_add_to_cart),
            mean_amount_of_unique_producers = mean(amount_of_unique_producers),
            mean_value_of_all_products_added = mean(value_of_all_products_added),
            mean_amount_of_checkouts = mean(amount_of_checkouts),
            mean_value_of_checkouts = mean(value_of_checkouts),
            mean_items_in_checkots = mean(items_in_checkouts),
            mean_amount_of_purchases = mean(amount_of_purchases),
            mean_value_of_purchases = mean(value_of_purchases),
            mean_items_in_purchases = mean(items_in_purchases))

session_data %>%
  filter(country=='Costa Rica') %>% 
  group_by(user_id) %>%
  summarise(amount_of_user_pseudo_id = n_distinct(user_pseudo_id)) %>% 
  group_by(amount_of_user_pseudo_id) %>% 
  summarise(count = n())
  



sd(users_data_tidy_filtered$sum_in_producer)
```


#3.4 Descriptive Statistics
```{r preprocessing, warning=F, message=F, echo=F}
# Here I am joining the experiment case and time in producer to the sessions dataframe

last_event_date <- as.Date('2024-01-01')

print(paste('total amount of sessions', nrow(sessions_data_tidy)))
print(paste('amount of sessions after',variable_min_event_date,':', nrow(
  sessions_data_tidy %>% 
    filter(event_date > variable_min_event_date)
  )))
print(paste('amount of sessions after',variable_min_event_date,'and before',last_event_date,':', nrow(
  sessions_data_tidy %>% 
    filter(event_date > variable_min_event_date,
           event_date < last_event_date)
  )))

print(paste('amount of sessions after',variable_min_event_date,'and before',last_event_date,'from Costa Rica:', nrow(
  sessions_data_tidy %>% 
    filter(event_date > variable_min_event_date,
           event_date < last_event_date,
           country == 'Costa Rica')
  )))


print(paste('amount of users after',variable_min_event_date,'and before',last_event_date,'from Costa Rica that never user the platform before',last_event_date,':', nrow(
  sessions_data_tidy %>% 
    filter(event_date > variable_min_event_date,
           event_date < last_event_date,
           country == 'Costa Rica') %>% 
    group_by(user_pseudo_id)
  )))

print(paste('total amount of users', nrow(users_data_tidy)))
print(paste('amount of users with first visit after',variable_min_event_date,':', nrow(
  users_data_tidy %>% 
    filter(experiment_case != -1,
           min_event_date > variable_min_event_date)
  )))


variable_max_event_date


print(paste('amount of sessions after',variable_min_event_date,'and before',variable_max_event_date,':', nrow(
  users_data_tidy %>% 
    filter(experiment_case != -1,
           min_event_date > variable_min_event_date,
           max_event_date < variable_max_event_date)
  )))

print(paste('amount of sessions after',variable_min_event_date,'and before',variable_max_event_date,'from Costa Rica:', nrow(
  users_data_tidy %>% 
    filter(country == 'Costa Rica',
         experiment_case != -1,
         min_event_date >= variable_min_event_date,
         max_event_date < variable_max_event_date)
  )))

```


#4-Visualize
#4.1-Filter data for analysis
```{r preprocessing, warning=F, message=F, echo=F}
# Using ggplot2 for the scatter plot
if (!require(ggplot2)) install.packages("ggplot2")
if (!require(dplyr)) install.packages("dplyr")
if (!require(patchwork)) install.packages("patchwork")


library(ggplot2)
library(dplyr)
library(patchwork)
library(flexplot)


users_data_tidy_filtered

a=flexplot( sum_in_producer~1, data=users_data_tidy_filtered)
b=flexplot(amount_of_session~1, data=users_data_tidy_filtered)
c=flexplot(value_of_purchases~1, data=users_data_tidy_filtered)
require(cowplot)
plot_grid(a,b,c, nrow=3)

a=flexplot(amount_of_session~experiment_case, data=users_data_tidy_filtered, method = "poisson", jitter = c(0,1))
b=flexplot(experiment_case~amount_of_session, data=users_data_tidy_filtered, method = "poisson", jitter = c(0,0))
plot_grid(a,b, nrow=1)




```

#4.2-Visualize Time in Producers
```{r preprocessing, warning=F, message=F, echo=F}
#Q-Q Plot of log(Time in Producer) with sum_in_producer > variable_min_time_in_producer
hist_log_plot_time_producer <- users_data_tidy_filtered %>% 
  ggplot(aes(x = (log(sum_in_producer)+1), fill = as.factor(experiment_case))) +
  geom_histogram(binwidth = 1, position = "dodge") +  # Adjust binwidth as needed
  facet_wrap(~experiment_case) +  # Create separate plots for each experiment_case
  labs(x = "Time in Producer", y = "Frequency", fill = "Experiment Case") +
  theme(plot.title = element_text(size = 10, face = "bold"),
                               plot.margin = margin(1, 1, 1, 1, "cm")) +  # Adjust margins as needed 
  ggtitle(paste("Histogram of log(Time in Producer) with sum_in_producer >", variable_min_time_in_producer))


#Q-Q Plot of Time in Producer with sum_in_producer > variable_min_time_in_producer
q_q_plot_time_producer <-  users_data_tidy_filtered %>% 
  ggplot(aes(sample = sum_in_producer)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~experiment_case) +  # Separate plots for each experiment_case
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles") +
  theme(plot.title = element_text(size = 10, face = "bold"),
                               plot.margin = margin(1, 1, 1, 1, "cm")) +  # Adjust margins as needed 
  ggtitle(paste("Q-Q Plot of Time in Producer with sum_in_producer >", variable_min_time_in_producer))


#Q-Q Plot of log(Time in Producer) with sum_in_producer > variable_min_time_in_producer
hist_plot_time_producer <- users_data_tidy_filtered %>% 
  ggplot(aes(x = (sum_in_producer), fill = as.factor(experiment_case))) +
  geom_histogram(binwidth = 1, position = "dodge") +  # Adjust binwidth as needed
  facet_wrap(~experiment_case) +  # Create separate plots for each experiment_case
  labs(x = "Time in Producer", y = "Frequency", fill = "Experiment Case") +
  theme(plot.title = element_text(size = 10, face = "bold"),
                               plot.margin = margin(1, 1, 1, 1, "cm")) + # Adjust margins as needed
  ggtitle(paste("Histogram of Time in Producer with sum_in_producer >", variable_min_time_in_producer))


#Q-Q Plot of log(Time in Producer) with sum_in_producer > variable_min_time_in_producer
q_q_log_plot_time_producer <- users_data_tidy_filtered %>% 
  ggplot(aes(sample = log(sum_in_producer)+1)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~experiment_case) +  # Separate plots for each experiment_case
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles") +
  theme(plot.title = element_text(size = 10, face = "bold"),
                               plot.margin = margin(1, 1, 1, 1, "cm")) +  # Adjust margins as needed 
  ggtitle(paste("Q-Q Plot of log(Time in Producer) with sum_in_producer >", variable_min_time_in_producer))

print(q_q_plot_time_producer)
print(q_q_log_plot_time_producer)
print(hist_plot_time_producer)
print(hist_log_plot_time_producer)
```

#4.3-Visualize Amount of Sessions
```{r preprocessing, warning=F, message=F, echo=F}
#Q-Q Plot of log(Time in Producer) with sum_in_producer > variable_min_time_in_producer
hist_log_plot_amount_sessions <- users_data_tidy_filtered %>% 
  ggplot(aes(x = (log(amount_of_session)+1), fill = as.factor(experiment_case))) +
  geom_histogram(binwidth = 1, position = "dodge") +  # Adjust binwidth as needed
  facet_wrap(~experiment_case) +  # Create separate plots for each experiment_case
  labs(x = "Time in Producer", y = "Frequency", fill = "Experiment Case") +
  theme(plot.title = element_text(size = 10, face = "bold"),
                               plot.margin = margin(1, 1, 1, 1, "cm")) +  # Adjust margins as needed 
  ggtitle(paste("Histogram of log(amount_of_session) with sum_in_producer >", variable_min_time_in_producer))


#Q-Q Plot of Time in Producer with sum_in_producer > variable_min_time_in_producer
q_q_plot_amount_sessions <-  users_data_tidy_filtered %>% 
  ggplot(aes(sample = amount_of_session)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~experiment_case) +  # Separate plots for each experiment_case
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles") +
  theme(plot.title = element_text(size = 10, face = "bold"),
                               plot.margin = margin(1, 1, 1, 1, "cm")) +  # Adjust margins as needed 
  ggtitle(paste("Q-Q Plot of amount_of_session with sum_in_producer >", variable_min_time_in_producer))


#Q-Q Plot of log(Time in Producer) with sum_in_producer > variable_min_time_in_producer
hist_plot_amount_sessions<- users_data_tidy_filtered %>% 
  ggplot(aes(x = (amount_of_session), fill = as.factor(experiment_case))) +
  geom_histogram(binwidth = 1, position = "dodge") +  # Adjust binwidth as needed
  facet_wrap(~experiment_case) +  # Create separate plots for each experiment_case
  labs(x = "Time in Producer", y = "Frequency", fill = "Experiment Case") +
  theme(plot.title = element_text(size = 10, face = "bold"),
                               plot.margin = margin(1, 1, 1, 1, "cm")) + # Adjust margins as needed
  ggtitle(paste("Histogram of amount_of_session with sum_in_producer >", variable_min_time_in_producer))


#Q-Q Plot of log(Time in Producer) with sum_in_producer > variable_min_time_in_producer
q_q_log_plot_amount_sessions <- users_data_tidy_filtered %>% 
  ggplot(aes(sample = log(amount_of_session)+1)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~experiment_case) +  # Separate plots for each experiment_case
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles") +
  theme(plot.title = element_text(size = 10, face = "bold"),
                               plot.margin = margin(1, 1, 1, 1, "cm")) +  # Adjust margins as needed 
  ggtitle(paste("Q-Q Plot of log(amount_of_session) with sum_in_producer >", variable_min_time_in_producer))

print(q_q_plot_amount_sessions)
print(q_q_log_plot_amount_sessions)
print(hist_plot_amount_sessions)
print(hist_log_plot_amount_sessions) 
```
#4.4- Visualize Purchase Events
```{r preprocessing, warning=F, message=F, echo=F}
# Using ggplot2 for the scatter plot

users_data_tidy_filtered %>%
  filter(value_of_purchases > 0) %>% 
  ggplot(aes(x = value_of_purchases/100, fill = as.factor(experiment_case))) +
  geom_histogram(binwidth = 1, position = "dodge") +  # Adjust binwidth as needed
  facet_wrap(~experiment_case) +  # Create separate plots for each experiment_case
  labs(x = "value_of_purchases/10000", y = "Frequency", fill = "Experiment Case") +
  theme_minimal()


users_data_tidy_filtered %>%
  filter(amount_of_purchases>0) %>% 
  ggplot(aes(x = value_of_purchases, y = sum_in_producer, color=experiment_case, shape=experiment_case)) +  # Corrected this line
  geom_point() +
  labs(x = "Value of Purchase", y = "Time in Producer", title = "Add to Cart vs. Producer Sum") +
  theme_minimal()  # This applies a minimal theme to the plot


users_data_tidy_filtered %>% 
  filter(amount_of_purchases > 0)

users_data_tidy_filtered %>%
  filter(amount_of_purchases>0) %>% 
  ggplot(aes(x = items_in_purchases, y = sum_in_producer, color=experiment_case, shape=experiment_case)) +  # Corrected this line
  geom_point() +
  labs(x = "Value of Purchase", y = "Time in Producer", title = "Add to Cart vs. Producer Sum") +
  theme_minimal()  # This applies a minimal theme to the plot

users_data_tidy_filtered %>%
  ggplot(aes(x = amount_of_session, y = sum_in_producer, color=experiment_case, shape=experiment_case)) +  # Corrected this line
  geom_point() +
  labs(x = "Amount of sessions", y = "Time in Producer", title = "Time in Producer vs Amount of Sessions") +
  theme_minimal()  # This applies a minimal theme to the plot



```
#4.5-Visualize Amount of Time Vs Purchase
```{r preprocessing, warning=F, message=F, echo=F}


```
#5-Hypothesis Testing
#5.2-Visualize Hypothesis
#5.2.1-Hypothesis 1,....
```{r preprocessing, warning=F, message=F, echo=F}
#Purchased data aggregated by user

users_data_tidy_filtered %>% 
ggplot(aes(x = experiment_case, y = log(sum_in_producer+1))) +
  geom_boxplot() +  # Add points
  labs(x = "experiment_case", y = "log(Time in Producers + 1)",
       title = "Experiment case vs Time in Producer") +
  theme_minimal()  # Minimal theme for aesthetics  

users_data_tidy_filtered %>% 
ggplot(aes(x = experiment_case, y = amount_of_session)) +
  geom_boxplot() +  # Add points
  labs(x = "experiment_case", y = "Sum of Amount of Sessions per user",
       title = "Sum of Amount of Sessions per user") +
  theme_minimal()  # Minimal theme for aesthetics  

users_data_tidy_filtered %>% 
  filter(value_of_purchases>0) %>% 
ggplot(aes(x = experiment_case, y = value_of_purchases)) +
  geom_boxplot() +  # Add points
  labs(x = "experiment_case", y = "Sum of Amount of Sessions per user",
       title = "Sum of Amount of Sessions per user") +
  theme_minimal()  # Minimal theme for aesthetics  

users_data_tidy_filtered %>% 
  filter(value_of_all_products_added>0) %>% 
ggplot(aes(x = experiment_case, y = value_of_all_products_added)) +
  geom_boxplot() +  # Add points
  labs(x = "experiment_case", y = "Sum of all products added to cart in CRC",
       title = "Sum of all products added to cart per user") +
  theme_minimal()  # Minimal theme for aesthetics  

users_data_tidy_filtered %>% 
  filter(value_of_checkouts>0) %>% 
ggplot(aes(x = experiment_case, y = value_of_checkouts)) +
  geom_boxplot() +  # Add points
  labs(x = "experiment_case", y = "Value of Checkouts in CRC",
       title = "Sum of all of Checkouts per user") +
  theme_minimal()  # Minimal theme for aesthetics  

```


#5.3-Hypothesis Statistical Testing
#5.3.0- Descriptive statistics
```{r preprocessing, warning=F, message=F, echo=F}
print(paste('amount of sessions after',variable_min_event_date,'and before',variable_max_event_date,':',nrow(
  sessions_data_tidy %>% 
  filter(event_date>variable_min_event_date,
         event_date<variable_max_event_date)
)))
print(paste('amount of users after',variable_min_event_date,'and before',variable_max_event_date,':',nrow(
  users_data_tidy %>% 
  filter(min_event_date>variable_min_event_date)
)))

print(paste('amount of users from Costa Rica with first visit after',variable_min_event_date,'and before',variable_max_event_date,':',nrow(
  users_data_tidy %>% 
  filter(experiment_case!=-1,
         min_event_date>=variable_min_event_date,
         min_event_date<variable_max_event_date)
)))

print(paste('amount of users from Costa Rica with first visit after',variable_min_event_date,'and before',variable_max_event_date,':',nrow(
  users_data_tidy %>% 
  filter(experiment_case!=-1,
         min_event_date>=variable_min_event_date,
         min_event_date<variable_max_event_date,
         country=='Costa Rica')
)))


print(paste('mean time in producer information from all users',mean(users_data_tidy_filtered$sum_in_producer),'with an SD of',sd(users_data_tidy_filtered$sum_in_producer),'with a total sample size of',nrow(users_data_tidy_filtered)))
print(paste('mean amount of session from all users',mean(users_data_tidy_filtered$amount_of_session),'with an SD of',sd(users_data_tidy_filtered$amount_of_session),'with a total sample size of',nrow(users_data_tidy_filtered)))
print(paste('mean value of pruchases from all users',mean(users_data_tidy_filtered$value_of_purchases),'with an SD of',sd(users_data_tidy_filtered$value_of_purchases),'with a total sample size of',nrow(users_data_tidy_filtered)))

users_data_tidy_filtered %>% 
  group_by(experiment_case) %>% 
  summarise(amount_of_users = n(),
            mean_time_producer = mean(sum_in_producer),
            SD_time_producer = sd(sum_in_producer))

users_data_tidy_filtered %>% 
  group_by(experiment_case) %>% 
  summarise(amount_of_users = n(),
            mean_amount_of_session = mean(amount_of_session),
            SD_amount_of_session = sd(amount_of_session))

users_data_tidy_filtered %>% 
  group_by(experiment_case) %>% 
  summarise(amount_of_users = n(),
            mean_value_of_purchases = mean(value_of_purchases),
            SD_value_of_purchases = sd(value_of_purchases))

users_data_tidy_filtered %>% 
  group_by(experiment_case) %>% 
  summarise(amount_of_users = n(),
            mean_amount_of_purchases = mean(amount_of_purchases),
            SD_amount_of_purchases = sd(amount_of_purchases))

users_data_tidy_filtered %>% 
  group_by(experiment_case) %>% 
  summarise(amount_of_users = n(),
            mean_value_of_value_of_checkouts = mean(value_of_checkouts),
            SD_value_of_value_of_checkouts = sd(value_of_checkouts))

users_data_tidy_filtered %>% 
  group_by(experiment_case) %>% 
  summarise(amount_of_users = n(),
            mean_amount_of_checkouts = mean(amount_of_checkouts),
            SD_amount_of_checkouts = sd(amount_of_checkouts))


users_data_tidy_filtered %>% 
  group_by(experiment_case) %>% 
  summarise(amount_of_users = n(),
            mean_value_of_all_products_added = mean(value_of_all_products_added),
            SD_value_of_all_products_added = sd(value_of_all_products_added))

users_data_tidy_filtered %>% 
  group_by(experiment_case) %>% 
  summarise(amount_of_users = n(),
            mean_amount_of_add_to_cart = mean(amount_of_add_to_cart),
            SD_amount_of_add_to_cart = sd(amount_of_add_to_cart))
```

#5.3.1-Checking for Assumptions
```{r preprocessing, warning=F, message=F, echo=F}
#Purchased data aggregated by user

# Install and load the necessary packages
if (!require(MASS)) install.packages("MASS")
if (!require(dplyr)) install.packages("dplyr")

library(MASS)
library(dplyr)

# Define the variable of interest
variable_of_interest <- "sum_in_producer"

# Define the experiment cases of interest
experiment_cases_of_interest <- c(0, 1, 2)

# Initialize an empty list to store results
results <- list()

# Specify a small constant to add (adjust based on your data's scale)
small_constant <- 1

users_data_tidy_filtered_sum_log <- users_data_tidy_filtered %>% 
  mutate(sum_in_producer = log(sum_in_producer+1))


# Loop through each specified experiment_case
for(case in experiment_cases_of_interest) {
  # Subset the data for the current case
  subset_data <- users_data_tidy_filtered %>%
    dplyr::select(variable_of_interest) %>%
    na.omit()  # Remove missing values

  # Shift the data by adding a small constant to ensure positivity
  subset_data[[variable_of_interest]] <- subset_data[[variable_of_interest]] + small_constant

  # Finding the optimal lambda for Box-Cox transformation
  bc <- boxcox(subset_data[[variable_of_interest]] ~ 1, plotit = FALSE)
  lambda_optimal <- bc$x[which.max(bc$y)]
  
  # Applying the Box-Cox transformation
  if (lambda_optimal != 0) {
    subset_data[[variable_of_interest]] <- (subset_data[[variable_of_interest]]^lambda_optimal - 1) / lambda_optimal
  } else {
    subset_data[[variable_of_interest]] <- log(subset_data[[variable_of_interest]])
  }
  
  # Check if there's enough data to perform the test
  if(length(subset_data[[variable_of_interest]]) > 3) {
    # Perform the Shapiro-Wilk test on the Box-Cox transformed data
    test_result <- shapiro.test(subset_data[[variable_of_interest]])
    results[[as.character(case)]] <- test_result  # Store results
  } else {
    results[[as.character(case)]] <- "Not enough data for the test"
  }
}

# View results
print(results)



```



#5.3.2-MANOVA Testing
```{r preprocessing, warning=F, message=F, echo=F}
# Install and load the necessary packages
if (!require(MASS)) install.packages("MASS")
library(MASS)

print("-----------------MANOVA-----------------")
mod <- manova(cbind(sum_in_producer, amount_of_session, value_of_purchases) ~ experiment_case, data = users_data_tidy_filtered)
summary(mod)
```


#5.3.3-Poshoc Value for sum_in_producer
```{r preprocessing, warning=F, message=F, echo=F}
print("-----------------Visualize-----------------")
linear=lm(sum_in_producer+1~experiment_case, data=users_data_tidy_filtered)
gm_gamma=glm(sum_in_producer+1~experiment_case, data=users_data_tidy_filtered, family = Gamma())
compare.fits(sum_in_producer+1~experiment_case, data=users_data_tidy_filtered, model1 = linear, model2 = gm_gamma)

a=flexplot(sum_in_producer~experiment_case, data=users_data_tidy_filtered, method = "Gamma", jitter = c(1,0.5))
a
plot_grid(a,b, nrow=1)

print("-----------------ANOVA: sum_in_producer-----------------")
anova_sum_in_product <- aov(log(sum_in_producer+1) ~ experiment_case, data = users_data_tidy_filtered)
summary(anova_sum_in_product)

print(paste('AIC of anova_sum_in_product:',AIC(anova_sum_in_product)))
print("-----------------glm_gaussian: sum_in_producer-----------------")
# Fitting a Gamma regression model
# glm_sum_in_product_gaussian_log <- glm(sum_in_producer +1 ~ as.factor(experiment_case),
#                                     family = gaussian(link = "log"),
#                                     data = users_data_tidy_filtered)
glm_sum_in_product_gaussian_identity <- glm(log(sum_in_producer+1) ~ as.factor(experiment_case),
                                         family = gaussian(link = "identity"),
                                         data = users_data_tidy_filtered)

# glm_sum_in_product_gaussian_inverse <- glm(log(sum_in_producer+1) ~ as.factor(experiment_case),
#                                         family = gaussian(link = "inverse"),
#                                         data = users_data_tidy_filtered)


# 
# print(paste('AIC of glm_sum_in_product_gaussian_log:',AIC(glm_sum_in_product_gaussian_log)))
print(paste('AIC of glm_sum_in_product_gaussian_identity:',AIC(glm_sum_in_product_gaussian_identity)))
# print(paste('AIC of glm_sum_in_product_gaussian_inverse:',AIC(glm_sum_in_product_gaussian_inverse)))
# Viewing the summary of the model
 summary(glm_sum_in_product_gaussian_identity)

print("-----------------glm_Gamma: sum_in_producer-----------------")
# Fitting a Gamma regression model
# glm_sum_in_product_gamma <- glm(sum_in_producer +1 ~ as.factor(experiment_case),
#                                     family = Gamma(),
#                                     data = users_data_tidy_filtered)
# 
# summary(glm_sum_in_product_gamma)

# glm_sum_in_product_gamma_log <- glm(sum_in_producer +1 ~ as.factor(experiment_case),
#                                     family = Gamma(link = "log"),
#                                     data = users_data_tidy_filtered)
# glm_sum_in_product_gamma_identity <- glm(sum_in_producer+1 ~ as.factor(experiment_case),
#                                          family = Gamma(link = "identity"),
#                                          data = users_data_tidy_filtered)

# glm_sum_in_product_gamma_inverse <- glm(sum_in_producer+1 ~ as.factor(experiment_case),
#                                         family = Gamma(link = "inverse"),
#                                         data = users_data_tidy_filtered)
# 
# print(paste('AIC of glm_sum_in_product_gamma_log:',AIC(glm_sum_in_product_gamma_log)))
print(paste('AIC of glm_sum_in_product_gamma_identity:',AIC(glm_sum_in_product_gamma_identity)))
# print(paste('AIC of glm_sum_in_product_gamma_inverse:',AIC(glm_sum_in_product_gamma_inverse)))
# Viewing the summary of the model
summary(glm_sum_in_product_gamma_identity)

# model.comparison(glm_sum_in_product_gamma_identity,sum_in_producer_cpglm_identity)

print("-----------------Tweedie_(cpglm)sum_in_producer-----------------")
sum_in_producer_cpglm_identity <- cpglm(sum_in_producer+1 ~ experiment_case, 
                     data = users_data_tidy_filtered, 
                     link = "identity")
# sum_in_producer_cpglm_log <- cpglm(sum_in_producer+1 ~ experiment_case, 
#                      data = users_data_tidy_filtered, 
#                      link = "log")
# sum_in_producer_cpglm_inverse <- cpglm(sum_in_producer+1 ~ experiment_case, 
#                      data = users_data_tidy_filtered, 
#                      link = "inverse")


print(paste('AIC of sum_in_producer_cpglm_identity:',AIC(sum_in_producer_cpglm_identity)))
# print(paste('AIC of sum_in_producer_cpglm_log:',AIC(sum_in_producer_cpglm_log)))
# print(paste('AIC of sum_in_producer_cpglm_inverse:',AIC(sum_in_producer_cpglm_inverse)))

# summary(sum_in_producer_cpglm_identity)

#print("-----------------sum_in_producer_cpglm_identity_case_1_and_2: sum_in_producer case 1 vs 2-----------------")
# users_data_tidy_filtered_case_1_and_2 <-users_data_tidy_filtered %>% 
#   filter(experiment_case!=0)
# 
# anova_sum_in_product_case_1_and_2 <- aov(log(sum_in_producer+1) ~ experiment_case, 
#                                          data = users_data_tidy_filtered_case_1_and_2)
# summary(anova_sum_in_product_case_1_and_2)
# AIC(anova_sum_in_product)
# 
# sum_in_producer_cpglm_identity_case_1_and_2 <- cpglm(sum_in_producer+1 ~ experiment_case, 
#                      data = users_data_tidy_filtered_case_1_and_2, 
#                      link = "identity")
# 
# summary(sum_in_producer_cpglm_identity_case_1_and_2)


```




#5.3.4-Poshoc Value of Purchase analysis with cpglm
```{r preprocessing, warning=F, message=F, echo=F}
if (!require(statmod)) install.packages("statmod")
if (!require(tweedie)) install.packages("tweedie")
if (!require(cplm)) install.packages("cplm")
# Assuming you have the 'cplm' package installed
library(cplm)
library(tweedie)
library(statmod)  # for tweedie.profile

amount_of_purchases_poisson <- glm(amount_of_purchases+1 ~ as.factor(experiment_case),
                                   family = poisson(),
                                   data = users_data_tidy_filtered_case_2_reference)

amount_of_purchases_poisson <- glm(amount_of_purchases+1 ~ as.factor(experiment_case),
                                   family = Gamma(link="identity"),
                                   data = users_data_tidy_filtered)


summary(amount_of_purchases_poisson)



print("-----------------gaussian: value_of_session-----------------")
# Fitting a Gamma regression model
value_of_purchases_gaussian_identity <- glm(log(value_of_purchases+1) ~ as.factor(experiment_case), 
                                            family = gaussian(link = "identity"), 
                                            data = users_data_tidy_filtered)
# value_of_purchases_gaussian_log <- glm(value_of_purchases+1 ~ as.factor(experiment_case), family = gaussian(link = "log"), data = users_data_tidy_filtered)
# value_of_purchases_gaussian_inverse <- glm(value_of_purchases+1 ~ as.factor(experiment_case), family = gaussian(link = "inverse"), data = users_data_tidy_filtered)

print(paste('AIC of value_of_purchases_gaussian_identity:',AIC(value_of_purchases_gaussian_identity)))
# print(paste('AIC of value_of_purchases_gaussian_log:',AIC(value_of_purchases_gaussian_log)))
# print(paste('AIC of value_of_purchases_gaussian_inverse:',AIC(value_of_purchases_gaussian_inverse)))


# Viewing the summary of the model
summary(value_of_purchases_gaussian_identity)




print("-----------------gamma: value_of_session-----------------")
# Fitting a Gamma regression model
value_of_purchases_gamma_log <- glm(value_of_purchases+1 ~ as.factor(experiment_case), 
                                    family = Gamma(link = "log"), 
                                    data = users_data_tidy_filtered)
value_of_purchases_gamma_identity <- glm(value_of_purchases+1 ~ as.factor(experiment_case), 
                                         family = Gamma(link = "identity"), 
                                         data = users_data_tidy_filtered)
value_of_purchases_gamma_inverse<- glm(value_of_purchases+1 ~ as.factor(experiment_case), 
                                       family = Gamma(link = "inverse"), 
                                       data = users_data_tidy_filtered)
# 
# print(paste('AIC of value_of_purchases_gamma_log:',AIC(value_of_purchases_gamma_log)))
# print(paste('AIC of value_of_purchases_gamma_identity:',AIC(value_of_purchases_gamma_identity)))
# print(paste('AIC of value_of_purchases_gamma_inverse:',AIC(value_of_purchases_gamma_inverse)))
# Viewing the summary of the model


print("-----------------glm_tweedie: value_of_session-----------------")

# Estimate the power parameter
power_estimate <- tweedie.profile(value_of_purchases ~ as.factor(experiment_case), 
                                  p.vec=seq(0, 3, by=0.1),
                                  data = users_data_tidy_filtered)

power_param <- power_estimate$p.max

print(paste('power parameter:',power_estimate$p.max))

value_of_purchases_glm_tweedie <- glm(value_of_purchases ~ experiment_case, 
                 family = tweedie(var.power = power_param),
                 data = users_data_tidy_filtered)

summary(value_of_purchases_glm_tweedie)


print ('----------cpglm_tweedie: value_of_session')

# Fit the Compound Poisson Generalized Linear Model
value_of_purchases_cpglm_log_identity <- cpglm(value_of_purchases ~ experiment_case, 
                     data = users_data_tidy_filtered, 
                     link = "identity")

# Fit the Compound Poisson Generalized Linear Model
value_of_purchases_cpglm_inverse <- cpglm(value_of_purchases ~ experiment_case, 
                     data = users_data_tidy_filtered, 
                     link = "inverse")

# Fit the Compound Poisson Generalized Linear Model
value_of_purchases_cpglm_log <- cpglm(value_of_purchases+1 ~ experiment_case, 
                     data = users_data_tidy_filtered, 
                     link = "log")




#---------------------users_data_tidy_filtered_case_2_reference

users_data_tidy_filtered_case_2_reference <- users_data_tidy_filtered %>%
  mutate(experiment_case = as.factor(experiment_case)) %>%
  mutate(experiment_case = relevel(experiment_case, ref = "2"))

value_of_purchases_cpglm_log_identity_case_2_reference <- cpglm(value_of_purchases ~ experiment_case, 
                     data = users_data_tidy_filtered_case_2_reference, 
                     link = "identity")



print(paste('AIC of value_of_purchases_cpglm_log_identity:',AIC(value_of_purchases_cpglm_log_identity_case_2_reference)))
print(paste('AIC of value_of_purchases_cpglm_inverse:',AIC(value_of_purchases_cpglm_log_identity)))
# print(paste('AIC of value_of_purchases_cpglm_log:',AIC(value_of_purchases_cpglm_log)))

summary(value_of_purchases_cpglm_log_identity_case_2_reference)

print ('----------cpglm_tweedie_case_1_and_2: value_of_session')

value_of_purchases_cpglm_identity_identity_case_1_and_2 <- cpglm(value_of_purchases ~ experiment_case, 
                     data = users_data_tidy_filtered_case_1_and_2_case_2_reference,
                     link = "identity")

users_data_tidy_filtered_case_1_and_2_case_2_reference <- users_data_tidy_filtered_case_1_and_2 %>% 
  mutate(experiment_case = as.factor(experiment_case)) %>%
  mutate(experiment_case = relevel(experiment_case, ref = "2"))

AIC(value_of_purchases_cpglm_identity_identity_case_1_and_2)
summary(value_of_purchases_cpglm_identity_identity_case_1_and_2)

anova_value_of_purchases_case_1_and_2 <- aov(log(value_of_purchases+1) ~ experiment_case, data = users_data_tidy_filtered_case_1_and_2)
AIC(anova_value_of_purchases_case_1_and_2)
summary(anova_value_of_purchases_case_1_and_2)



# ------------------------------------
# Assuming 'model' is your fitted GLM model
# Calculate standardized residuals
std_residuals <- rstandard(value_of_purchases_cpglm_log_identity)

# Extract residuals from the model
residuals <- residuals(value_of_purchases_cpglm_log_identity)

# You need to obtain the standard errors of the residuals. This might be done by looking at the
# summary or the model object itself to see if standard errors are available. This is just an example:
std_errors <- sqrt(summary(value_of_purchases_cpglm_log_identity)$dispersion)

# Now, calculate the standardized residuals
std_residuals <- residuals / std_errors

# From here, you would follow the previously given code to filter your data.


# Create a logical vector where TRUE indicates a standardized residual greater than 3
high_residuals <- abs(std_residuals) > 2

# Subset your original data frame to only include these high-residual observations
high_residuals_df <- users_data_tidy_filtered[high_residuals, ]

# Print the new data frame with outliers
print(high_residuals_df)
# ------------------------------------

# Residuals vs Fitted values
plot(predict(value_of_purchases_cpglm_log_identity), residuals(value_of_purchases_cpglm_log_identity, type = "response"),
     xlab = "Fitted values", ylab = "Residuals",
     main = "Residuals vs Fitted")
abline(h = 0, col = "red")

# QQ plot of residuals
qqnorm(residuals(value_of_purchases_gamma_identity, type = "response"))
qqline(residuals(value_of_purchases_gamma_identity, type = "response"), col = "red")

# Observed deviance
obs_deviance <- 401.81

# Degrees of freedom
df_residual <- 1741

# Chi-squared test
p_value <- pchisq(obs_deviance, df = df_residual, lower.tail = FALSE)

cat("P-value for Chi-squared test:", p_value, "\n")

# Install and load necessary package
if (!require("car")) install.packages("car")
library(car)

# Influence Plot
influencePlot(value_of_purchases_gamma_identity, id.method = "identify", main = "Influence Plot",
              sub = "Circle size is proportional to Cook's distance")
# Assuming 'users_data_tidy_filtered' is your data frame
outlier_indices <- c(1593, 1131)
outliers <- users_data_tidy_filtered[outlier_indices, ]

# Print the outliers to the R console
print(outliers)

```


#5.3.5-Poshoc  amount of session with poisson
```{r preprocessing, warning=F, message=F, echo=F}
#print("\n-----------------ANOVA: amount_of_session-----------------")
# anova_sum_in_product <- aov(log(amount_of_session+1) ~ experiment_case,
#                            data = users_data_tidy_filtered)
# summary(anova_sum_in_product)
glm_amount_of_session_gaussian <- glm(log(amount_of_session) ~ as.factor(experiment_case),
                                            family = gaussian(),
                                            data = users_data_tidy_filtered)
summary(glm_amount_of_session_gaussian)

#print("\n-----------------glm_gamma: amount_of_session-----------------")
glm_amount_of_session_gamma_identity <- glm(amount_of_session ~ as.factor(experiment_case),
                                            family = Gamma(link = "identity"),
                                            data = users_data_tidy_filtered)

summary(glm_amount_of_session_gamma_identity)

#print("\n-----------------glm_poisson: amount_of_session-----------------\n")
#glm_amount_of_session_poisson_log <- glm(amount_of_session ~ as.factor(experiment_case), 
#                                         family = poisson(link = "log"), 
#                                         data = users_data_tidy_filtered)

glm_amount_of_session_poisson_identity <- glm(amount_of_session ~ as.factor(experiment_case),
                                             family = poisson(link = "identity"),
                                             data = users_data_tidy_filtered)

#glm_amount_of_session_poisson_sqrt <- glm(amount_of_session ~ as.factor(experiment_case), 
#                                          family = poisson(link = "sqrt"), 
#                                          data = users_data_tidy_filtered)

#print(paste('AIC of glm_amount_of_session_poisson_log:',AIC(glm_amount_of_session_poisson_log)))
#print(paste('AIC of glm_amount_of_session_poisson_identity:',AIC(glm_amount_of_session_poisson_identity)))
#print(paste('AIC of glm_amount_of_session_poisson_sqrt:',AIC(glm_amount_of_session_poisson_sqrt)))

#summary(glm_amount_of_session_poisson_log)
summary(glm_amount_of_session_poisson_identity)
#summary(glm_amount_of_session_poisson_sqrt)


# print ('\n-----------------tweedie_cpglm: amount_of_session')
# Fit the Compound Poisson Generalized Linear Model
# amount_of_sessions_cpglm_identity <- cpglm(amount_of_session ~ experiment_case, 
#                      data = users_data_tidy_filtered, 
#                      link = "identity")

#amount_of_sessions_cpglm_log <- cpglm(amount_of_session ~ experiment_case, 
#                     data = users_data_tidy_filtered, 
#                     link = "log")

#amount_of_sessions_cpglm_sqrt <- cpglm(amount_of_session ~ experiment_case, 
#                     data = users_data_tidy_filtered, 
#                     link = "sqrt")


# print(paste('AIC of amount_of_sessions_cpglm_identity:',AIC(amount_of_sessions_cpglm_identity)))
#print(paste('AIC of amount_of_sessions_cpglm_log:',AIC(amount_of_sessions_cpglm_log)))
#print(paste('AIC of amount_of_sessions_cpglm_sqrt:',AIC(amount_of_sessions_cpglm_sqrt)))

# summary(amount_of_sessions_cpglm_identity)
#summary(amount_of_sessions_cpglm_log)
#summary(amount_of_sessions_cpglm_sqrt)

# print ('\n-----------------tweedie_glm: amount_of_session')
# Estimate the power parameter
#power_estimate <- tweedie.profile(amount_of_session ~ as.factor(experiment_case), 
#                                  p.vec=seq(1, 5, by=1),
#                                  data=users_data_tidy_filtered)
#power_param <- power_estimate$p.max

#print(paste('power parameter:',power_estimate$p.max))

# value_of_purchases_tweedie <- glm(amount_of_session ~ as.factor(experiment_case),
#                 family = tweedie(var.power = power_param),
#                 data = users_data_tidy_filtered)


#summary(value_of_purchases_tweedie)

print ('\n-----------------Graphical Analysis of best fitted model')

# INPUT CANDIDATE MODEL HERE!!!!
variable_selected_model <- value_of_purchases_tweedie

# Residuals vs Fitted values
plot(predict(variable_selected_model), residuals(variable_selected_model, type = "response"),
     xlab = "Fitted values", ylab = "Residuals",
     main = "Residuals vs Fitted variable_selected_model")
abline(h = 0, col = "red")

# QQ plot of residuals
qqnorm(residuals(variable_selected_model, type = "response"))
qqline(residuals(variable_selected_model, type = "response"), col = "red")

# ------------------------------------Plot High Residuals Cooks distance
# Install and load necessary package
if (!require("car")) install.packages("car")
library(car)

# Influence Plot
influencePlot(variable_selected_model, id.method = "identify", main = "Influence Plot",
              sub = "Circle size is proportional to Cook's distance")


print ('\n-----------------P-value for Chi-squared testl')

# Assuming 'model' is your fitted GLM model

# Extract observed deviance
obs_deviance <- deviance(variable_selected_model)

# Calculate degrees of freedom for residuals
# Total number of observations
n_obs <- nrow(variable_selected_model$data)

# Number of model parameters (including intercept)
# You can use length(coef(model)) or access the model's df.residual directly
n_params <- length(coef(variable_selected_model))
# Alternatively, use:
# n_params <- df.residual(model) + 1

# Calculate degrees of freedom for residuals
df_residual <- n_obs - n_params

# Print the values
cat("Observed Deviance:", obs_deviance, "\n")
cat("Degrees of Freedom for Residuals:", df_residual, "\n")

# Chi-squared test
p_value <- pchisq(obs_deviance, df = df_residual, lower.tail = FALSE)
cat("P-value for Chi-squared test:", p_value, "\n")
# ------------------------------------Print High Residuals
# Assuming 'model' is your fitted GLM model
# Calculate standardized residuals
std_residuals <- rstandard(variable_selected_model)

# ------------------------------------Print retrieve std_residuals for cplm object class

# Extract residuals from the model
# residuals <- residuals(variable_selected_model)

# You need to obtain the standard errors of the residuals. This might be done by looking at the
# summary or the model object itself to see if standard errors are available. This is just an example:
# std_errors <- sqrt(summary(variable_selected_model)$dispersion)

# Now, calculate the standardized residuals
# std_residuals <- residuals / std_errors


# ------------------------------------Continue with high residuals
# Create a logical vector where TRUE indicates a standardized residual greater than 3
high_residuals <- abs(std_residuals) > 3

# Subset your original data frame to only include these high-residual observations
high_residuals_df <- users_data_tidy_filtered[high_residuals, ]

# Print the new data frame with outliers
print(high_residuals_df)

# ------------------------------------Creates new df excluding datapoints with high residuals


# Create a logical vector where TRUE indicates a standardized residual less than 3
low_residuals <- abs(std_residuals) < 3
# Subset your original data frame to only include these low-residual observations
users_data_tidy_filtered_low_residuals_df <- users_data_tidy_filtered[low_residuals, ]

# Print the new data frame without outliers
print(users_data_tidy_filtered_low_residuals_df)




print("-----------------New modeling with data with no outliers-----------------")

selected_model_without_outliers <- glm(amount_of_session ~ as.factor(experiment_case),
                                           family = Gamma(link = "identity"),
                                           data = users_data_tidy_filtered_low_residuals_df)

selected_model_without_outliers <- glm(amount_of_session ~ as.factor(experiment_case),
                family = tweedie(var.power = power_param),
                data = users_data_tidy_filtered_low_residuals_df)

# selected_model_without_outliers <- cpglm(amount_of_session ~ experiment_case, 
#                      data = users_data_tidy_filtered_low_residuals_df, 
#                      link = "identity")





summary(variable_selected_model)
summary(selected_model_without_outliers)

# Residuals vs Fitted values
plot(predict(glm_amount_of_session_gamma_identity_low_residuals), residuals(glm_amount_of_session_gamma_identity_low_residuals, type = "response"),
     xlab = "Fitted values", ylab = "Residuals",
     main = "Residuals vs Fitted glm_amount_of_session_gamma_identity_low_residuals")
abline(h = 0, col = "red")

# QQ plot of residuals
qqnorm(residuals(glm_amount_of_session_gamma_identity_low_residuals, type = "response"))
qqline(residuals(glm_amount_of_session_gamma_identity_low_residuals, type = "response"), col = "red")

# Influence Plot
influencePlot(glm_amount_of_session_gamma_identity_low_residuals, id.method = "identify", main = "Influence Plot",
              sub = "Circle size is proportional to Cook's distance")


print(paste('mean total amount of sessions:',mean(users_data_tidy_filtered$amount_of_session)))
print(paste('var total amount of sessions:',var(users_data_tidy_filtered$amount_of_session)))
shape_amount_sessions = (mean(users_data_tidy_filtered$amount_of_session)^2)/var(users_data_tidy_filtered$amount_of_session)
print(paste('var total amount of sessions:',shape_amount_sessions))


# print("-----------------Visualy inspecting amount of sessions-----------------")
# glm_total_amount_session <- glm(users_data_tidy_filtered$amount_of_session~1, family = Gamma(link=identity))
# sumary_glm_total_amount_session<-summary(glm_total_amount_session)
# 
# users_data_tidy_filtered_only_0 <- users_data_tidy_filtered %>% 
#   filter(experiment_case == 0)
# glm_0_amount_session <- glm(amount_of_session~1, 
#                             family = Gamma(link=identity),
#                             data = users_data_tidy_filtered_only_0)
# sumary_glm_0_amount_session<-summary(glm_0_amount_session)
# print(sumary_glm_0_amount_session)
# 
# users_data_tidy_filtered_only_1 <- users_data_tidy_filtered %>% 
#   filter(experiment_case == 1)
# glm_1_amount_session <- glm(amount_of_session~1, 
#                             family = Gamma(link=identity),
#                             data = users_data_tidy_filtered_only_1)
# sumary_glm_1_amount_session<-summary(glm_1_amount_session)
# 
# 
# users_data_tidy_filtered_only_2 <- users_data_tidy_filtered %>% 
#   filter(experiment_case == 2)
# glm_2_amount_session <- glm(amount_of_session~1, 
#                             family = Gamma(link=identity),
#                             data = users_data_tidy_filtered_only_2)
# sumary_glm_2_amount_session<-summary(glm_2_amount_session)
# 
# shape_total <- 1/sumary_glm_total_amount_session$dispersion
# scale_total <- as.numeric(coef(glm_total_amount_session))/shape_total
# 
# shape_0 <- 1/sumary_glm_0_amount_session$dispersion
# scale_0 <- as.numeric(coef(glm_0_amount_session))/shape_0
# print(scale_0)
# 
# shape_1 <- 1/sumary_glm_1_amount_session$dispersion
# scale_1 <- as.numeric(coef(glm_total_amount_session))/shape_1
# 
# shape_2 <- 1/sumary_glm_2_amount_session$dispersion
# scale_2 <- as.numeric(coef(glm_1_amount_session))/shape_2
# 
# 
# hist(users_data_tidy_filtered$amount_of_session, freq = FALSE, ylim = c(0, 0.1))
# # curve(dgamma(x, shape = shape_total, scale = scale_total), from = 0, to = 10, 
# #       col = "red", add = TRUE)
# curve(dgamma(x, shape = shape_0, scale = scale_0), from = 0, to = 20, 
#       col = "blue", add = TRUE)
# curve(dgamma(x, shape = shape_1, scale = scale_1), from = 0, to = 20, 
#       col = "purple", add = TRUE)
# curve(dgamma(x, shape = shape_2, scale = scale_2), from = 0, to = 20, 
#       col = "red", add = TRUE)
summary(glm_amount_of_session_gamma_identity)
summary(glm_total_amount_session)

```
#5.3.3-Mediation Testing
```{r preprocessing, warning=F, message=F, echo=F}
if (!require(mediation)) install.packages("mediation")
library(mediation)
users_data_tidy_filtered_mediation_analysis <- users_data_tidy_filtered %>% 
  mutate(sum_in_producer = sum_in_producer+10,
         experiment_case = as.factor(experiment_case),
         value_of_purchases = value_of_purchases + 1)

glm_sum_in_product_gamma_identity <- glm(sum_in_producer ~ experiment_case,
                                         family = Gamma(link = "identity"),
                                         data = users_data_tidy_filtered_mediation_analysis)

glm_amount_of_session_gamma_identity <- glm(amount_of_session ~ experiment_case,
                                            family = Gamma(link = "identity"),
                                            data = users_data_tidy_filtered_mediation_analysis)

glm_amount_of_session_vs_time_gamma_identity <- glm(amount_of_session ~ sum_in_producer,
                                            family = Gamma(link = "identity"),
                                            data = users_data_tidy_filtered_mediation_analysis)
summary(glm_amount_of_session_vs_time_gamma_identity)

fit.totaleffect <- glm_amount_of_session_gamma_identity
fit.mediator <- glm_sum_in_product_gamma_identity

fit.dv <- glm(amount_of_session ~ experiment_case + sum_in_producer, 
                       family = Gamma(link = "identity"), 
                       data = users_data_tidy_filtered_mediation_analysis)

summary(fit.totaleffect)
summary(fit.mediator)
summary(fit.dv)

results = mediate(fit.mediator, fit.dv, treat='experiment_case', mediator='sum_in_producer',  sims = 1000)

summary(results)

a=flexplot(amount_of_session~sum_in_producer | experiment_case, data=users_data_tidy_filtered,
           method = "poisson", se=F,
           ghost.line = "gray",ghost.reference = list(experiment_case=0))
a

b=flexp lot(value_of_purchases~sum_in_producer | experiment_case, data=users_data_tidy_filtered,
           method = "poisson", se=F,ghost.line = "gray",ghost.reference = list(experiment_case=0))
b

```


